---
title       : Emigrating - Better off ?
subtitle    : DDP Slidify Assignment
author      : Pramesh Rogbeer
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
### 1. The Application 

**APPLICATION** :     [DDPFinal](https://pramesh.shinyapps.io/DDPFinal) located at https://pramesh.shinyapps.io/DDPFinal/

**OBJECTIVE**: Provide you with a few predictions on what to expect if you plan to emigrate.

**DATA** : Census data (and report) from 2013 was downloaded from the [UNDP site](http://hdr.undp.org/en/data) 



- The UNDP collects data from all over the world to calculate an annual  ***Human Development Index*** (HDI) for each country. This index provides a measure of people's wellbeing in different parts of the world. The HDI is made up of various independent indices. 

- The [DDPFinal](https://pramesh.shinyapps.io/DDPFinal) application uses a selection of these indices , but can be effortlessly modified to use a wider range .

- The [DDPFinal](https://pramesh.shinyapps.io/DDPFinal) application "predicts" how, compared to now, your quality of life could improve/degrade if you emigrated elsewhere

- the results are provided in tabular and graphical forms


Have fun !!



--- .class #id 

### 2. The Logic

### INPUT:  
 At the user interface: (1) your `current location` (2) where you want to `emigrate` , and (3) your `gender`. (Gender has an impact too - you can try it)

### OUTPUT: 
The output gives you the % change ( +ve or -ve) to expect in 12 different indicators. (e.g. life expectancy, taxation. etc.).The Computation is quite straighforward  :

`Result = (Value for Current Location - Value for Destination ) ` 

### RESULTS:
The results are presented in:

- a table (all values are in %)
- a histogram with values `>0` (improvements) and `<0` (loss in quality)




--- .class #id 

### 3. The coding
Some key points of the code : the full code is on my [github](https://github.com/Pramesh1/DDSlide2)  
(I set `echo=FALSE` to hide the code - it is too long)

For this presentation, I preset the input variables as follows:
```{r,eval=FALSE }
countryNow="Mauritius"
countryFuture="Germany"
gender="Male"

```


Output Result:
(Please take a look at the app on shiny.io to get an explanation of the result)

```{r,echo=FALSE }

library(shiny)
library(xtable)
# Load data ----
mdata<-read.csv("ddprod-pr.csv", header=TRUE)
mdata[,1]<-as.character(mdata[,1])  # preprocess data

countryNow="Mauritius"
countryFuture="Germany"
gender="Male"



        
        my.now<-mdata[grep(countryNow,mdata$country),]
        my.fut<-mdata[grep(countryFuture,mdata$country),]
        country.n<-my.now[,1]
        country.f<-my.fut[,1]
        
        m<-c(2,3,5,6,8,10,11,12,13,14,15,16)   # remove country name
        f<-c(2,3,4,6,7,9,11,12,13,14,15,16)
        
        if(gender=="Male"){                      
                data.now<-my.now[,m] 
                data.fut<-my.fut[,m] 
                
        } else {
                data.now<-my.now[,f]
                data.fut<-my.fut[,f] 
        }
        
        names(data.now)[3] <- "hdi"
        names(data.fut)[3] <- "hdi"
        names(data.now)[5] <- "le"
        names(data.fut)[5] <- "le"
        names(data.now)[6] <- "gni"
        names(data.fut)[6] <- "gni"
        
        data.result<-data.now-data.fut
        data.result$hdi.gii<-data.result$hdi.gii*-1
        data.result$hdi<-data.result$hdi*-1
        data.result$taxes<-data.result$taxes*-1
        data.result$cpi<-data.result$cpi*-1
        
        give.result<-data.result
        yy<-(data.result/data.now)*100
        data.result[,1:6]<-yy[,1:6] # convert all to percentages
        data.result[,8]<-yy[,8]
        data.result<-round(data.result,1)
        
        for (i in 1:12)
        {
                if (give.result[i]<0) {give.result[i] = "Worse"}
                else{give.result[i] ="BETTER!"}
        }            
        
        
        youresult<-rbind(data.result,give.result)      
        
        
        if (countryNow==countryFuture) {
                ymessage <- "Sorry , You do not seem to be relocation outside of your current country"
        } else {
                ymessage <- "Here is what awaits you: "
        } 
      
 youresult

```


--- .class #id 

### 4. CHALLENGES:

The `csv` data was loaded into a variable in the `server.R` file. But is was impossible to `dynamically` pass a list (countries listing) to the input part of the `ui.R` file. This problem could not be solved despite intensive search on the web.
I finally ended up building this list inside the `ui.R` file itself. 

Then there was the famous `UTF-8` encoding problem ... The app was not launching on the shiny server even though it was working perfectly on my laptop. After some search , I found out that I had to save the files with `UTF-8` encoding. Once this done, everything came back to normal.


I enjoyed this project quite a lot.

The application can be further improved. For example , a color scheme can be used for the histogram, e.g. GREEN for `>0` and RED for `<0` . 

